Viscoelastic Kelvin-Helmholtz instability

### 2016-02-12 paper/paper.tex
updated the paper, improved discussion of the wall dependence.

%	paper.tex	Toby Searle
%	Last modified: Fri 22 Jan 15:20:25 2016
%	using jfm template

@@

\section{Problem formulation}

We present a linear stability analysis of the Kelvin-Helmholtz instability in
the purely elastic regime using direct numerical simulation of both the
Oldroyd-B and FENE-P constitutive models for a polymeric fluid. The purely
elastic fluid is found to be unstable at sufficiently high Weissenberg number,
the key dimensionless number for turbulence without inertia in viscoelastic
flows. This is the ratio of the normal stress to the shear stress of the
polymeric component of the fluid $Wi = \frac{N_{1}}{\sigma} = \lambda
\dot{\gamma}$ where $\dot{\gamma}$ is the shear rate.  The growth rate of the
largest growing eigenmode of the instability is found to increase with
increasing Weissenberg number for low Reynold's number. This behaviour is
consistent across both the Oldroyd-B and FENE-P models.

The system we use for our analysis uses a hyperbolic tangent shaped laminar
profile for the streamwise velocity across a channel, where the instability
takes place between $y = \pm \Delta$. $y=0$ is the centreline of the channel,
so that if $\Delta << 1$ the flow can be said to be a free shear instability.
This gives a base flow profile, 
\begin{align} 
    U(y) &= \tanh \left( y/\Delta
    \right) \coth \left( 1/\Delta \right) \nonumber\\ V &= 0 \nonumber \\
    T_{xx}(y) &= 2 Wi \left( \dy{U} \right)^{2} \nonumber \\ T_{xy}(y) &=
    \dy{U} \nonumber \\ T_{yy}(y) &= 0 \nonumber \label{eq:KH_laminar_profile}
\end{align}
$U$ and $V$ are the base streamwise (x) and wall normal (y) velocities
respectively. $T$ is the base stress tensor. We use Gauss-Labatto points in the
wall-normal ($y$) direction for the base profile, and decomposed the
disturbances to this flow into Fourier modes.  
\begin{equation} 
    g(y) = \sum\limits_{n=-N}^{N} \widetilde{g}(y) e^{ikx + \lambda t} 
\end{equation}
for all disturbance variables $g = u, v, p, \tau_{i,j}$. Where $N$ is the
number of Fourier modes, $k$ is the streamwise wavenumber of the disturbance
and $\lambda$ is the growth rate of the mode. This program uses two domains of
pseudo-spectral points to give increased resolution in the centre of the
simulation. The simulation was also repeated using a code for which the system
of points was stretched using: 
\begin{align} 
    z_{u} &= \frac{y_{u}}{1-y_{u}} \\
    z_{b} &= \frac{y_{b}}{1+y_{b}} \\ U     &= \tanh{z/\Delta}
    \label{eq:KH_inf_profile} 
\end{align} 
This system ought to be completely insensitive to the boundary conditions at
the walls so we refer to it as 'free shear' throughout this manuscript.

The dimensionless quantities used throughout are non-dimensionalised relative
to the instability size, $\Delta$, rather than the total simulation size. The
obvious reason for this is that $\Delta$ is the length scale for the free shear
instability.

In order to simulate this flow, we used an Oldroyd-B fluid with very low
Reynolds number $\Rey \leq 0.01$ and a small ratio between the solvent and total
viscosities $\beta = \frac{\mu_{s}}{\mu_{s}+\mu_{p}}$. This approximates a
purely elastic fluid, where the polymer contribution to the stress on the fluid
is much larger  than the solvent contribution. The Oldroyd-B Navier stokes and
constitutive equations are then: 
\begin{align} 
    Re \left[ \dt{\mathbf{v}} +
    \mathbf{v} \cdot \nabla  \mathbf{v} \right] &= - \nabla p + \beta
    \nabla^{2} \mathbf{v} + \frac{1-\beta}{Wi} \nabla \cdot \mathbf{\tau} \\
    \dot{\tau}/Wi + \overset{\nabla}\tau &= \left(\nabla \mathbf{v}\right)^{T}
    + \nabla{\mathbf{v}} 
\end{align} 
With $\mathbf{v}$ as the total (base flow and disturbance) velocity and $\tau$
as the total stress in the polymeric fluid. The FENE-P viscoelastic fluid has
the advantage of being similarly easy to simulate, but also including a finite
extensibility for the polymers. This leads to a stress which depends on a
conformation tensor ($\mathbf{C}$) for the polymer dumbbells via a non-linear
spring force:

\begin{equation} \mathbf{\tau} = \frac{1-\frac{3}{L^{2}}}{1 +
	\frac{L^{2}}{tr(\mathbf{C^{2}})}} \end {equation}

\begin{figure} 
    \centering 
    \includegraphics[width=0.3\textwidth]{KH_diagram}
    \caption{diagram of the system} 
    \label{fig:diagram} 
\end{figure}

@@

\section{A purely elastic instability}

At low Reynolds number, low $\beta$ and sufficiently large Weissenberg number
we observe an instability across a range of streamwise disturbance wavenumbers.
This leads us to suppose that this instability might be a plausible cause for a
self-sustaining process in viscoelastic plane Couette flow, similar to that
observed by Waleffe.

The instability remains unchanged under variation of $\Delta$ at low $\Delta$,
proving that it is a free shear instability. Although the instability appears
to require some inertia in the fluid, it is still present for  $\Rey = 0.01$,
far lower than the usual threshold of $\Rey = 1000$ for a Newtonian
Kelvin-Helmholtz instability.

We see an instability grow from around $k \sim 0.06$ and move to lower $k$ as
the Weissenberg number increases (figure \ref{fig:dispersions_low_Re}). The
height of the instability also increases with increasing Weissenberg number
(figure \ref{fig:inf_low_Re}).

\begin{figure} 
    \centering 
    \begin{subfigure}[b]{0.48\textwidth} 
	\centering
	\includegraphics[width=\textwidth]{inf_purely_elastic} 
	\caption{}
	\label{fig:inf_low_Re} 
    \end{subfigure} ~
    \begin{subfigure}[b]{0.48\textwidth} 
	\centering
	\includegraphics[width=\textwidth]{inf_dispersions_low_Re} 
	\caption{}
	\label{fig:dispersions_low_Re} 
    \end{subfigure} 
    \caption{
	a) Free shear version of the instability. Plot of the maximum growth
	rate against Weissenberg number at $\Rey = 0.01$. b) Dispersion
	relations at various Weissenberg numbers to accompany the trend in
	figure a).
    } 
\end{figure}

@@

\begin{figure} 
    \centering 
    \begin{subfigure}[b]{0.48\textwidth} 
	\centering
	\includegraphics[width=\textwidth]{inf_vary_Re} 
	\caption{}
	\label{fig:inf_vary_Re} 
    \end{subfigure} ~
    \begin{subfigure}[b]{0.48\textwidth} 
	\centering
	\includegraphics[width=\textwidth]{inf_dispersions_low_Wi} 
	\caption{}
	\label{fig:dispersions_low_Wi} 
    \end{subfigure} 
    \caption{ 
	a) Free shear version of the instability. Plot of the maximum growth
	rate against Reynold's number with $\Wi=50$. b) Dispersion relations at
	various Reynold's numbers to accompany the trend in figure a).  
    }
\end{figure}

As the Reynold's number is reduced, new eigenvalues become dominant. Although
the dominant eigenvalue changes the flow is still unstable, even down to $\Rey
= 0.01$ (see figures \ref{fig:inf_vary_Re} and \ref{fig:dispersions_low_Wi}).

\subsection{ Shear instability with walls}

If we examine the eigenvectors of the instability, we see that there are very
large polymer stresses in the $\pm \Delta$ region. This corresponds to the
large shear rate brought about as the two flows pass each other. Examining the
flow field, we see that there are large vortices arranged with opposite
rotational directions above and below the shear region which extend almost to
the walls.

\begin{figure} \begin{subfigure}[b]{\textwidth} 
	\centering
	\includegraphics[width=\textwidth]{psi_low_delta}
	\caption{}
	\label{fig:psi_low_delta}
    \end{subfigure} \vspace{1 mm}
    \begin{subfigure}[b]{\textwidth}
	\centering
	\includegraphics[width=\textwidth]{txx_low_delta} 
	\caption{}
	\label{fig:stress_low_delta} 
    \end{subfigure} 
    \caption{
	a) Streamfunction of the largest eigenfunction of the instability when
	$\Rey = 0.1$, $\Wi =100$, $\Delta = 0.005$. Red is positive
	(streamlines of the flow point clockwise around the contours), Blue is
	negative (streamlines of the flow point anticlockwise around the
	contours) b) xx stress for the same instability.  
    }
\end{figure}

Dependence of the instability on the channel walls persists at very small
$\Delta$ whilst in the purely elastic region of the flow phase space. We are
not sure why this is. We might be able to understand this by thinking about shear
waves in an elastic solid? (was thinking about surface Rayleigh waves)

\begin{figure} 
    \centering 
    \includegraphics[width=\textwidth]{KH_vary_delta}
    \caption{
	Dispersion relations for various values of $\Delta$ at $\Rey = 0.1$,
	$\Wi = 100$. The sensitivity to the walls seems only to increase the
	strength of the instability. Even when the system is insensitive to the
	walls, at $\Delta= 0.0125$, there is still an instability present.
    } 
    \label{fig:walls_dependence} 
\end{figure}

\begin{figure} 
    \centering 
    \includegraphics[width=\textwidth]{psi_high_delta}
    \caption{ 
	Streamfunction of the eigenfunction of the instability at $\Delta =
	0.1$, $\Wi = 100$, $\Rey=0.1$. The magnitude is scaled by the xx stress
	in the centre of the channel.  
    } 
    \label{fig:psi_high_delta}
\end{figure}

@@

The reason we have have the simulation with the walls at all is because of the
implications for the plane Couette problem. The Kelvin-Helmholtz instability in
the Newtonian problem takes place on a length scale of about 10\% of the width
of the channel, or $\Delta = 0.1$. If this length scale is similar in the
purely elastic case, we can make say that the viscoelastic Kelvin-Helmholtz
instability is sensitive to the walls at this $\Delta$ and a $\Rey \lesssim 1$
(see figure \ref{fig:vary_Re_delta_conv}). This means that on the scale of the
channel, $\Rey \gtrsim 10$ for the walls not to affect the instability. So, the
important results for the purely elastic instability from the point of view of
the plane Couette problem are probably those for which the walls are relevant.

\begin{figure} \centering
    \includegraphics[width=0.7\textwidth]{vary_Re_delta_conv} \caption{ The
	blue line is the data from the free shear system and the green line is
	the $\Delta = 0.1$ data. By $\Rey = 1$ it is clear that the Reynold's
	number is sufficient such that the walled system behaves as though it
    were insensitive to the walls.  } \label{fig:vary_Re_delta_conv}
\end{figure}

At $\Delta = 0.1$ we see the same instability as that seen in the completely
free case.

\begin{figure} 
    \centering 
    \begin{subfigure}[b]{0.48\textwidth} 
	\centering
	\includegraphics[width=\textwidth]{KH_low_Re_vary_Wi} 
	\caption{}
	\label{fig:KH_purely_elastic} 
    \end{subfigure} ~
    \begin{subfigure}[b]{0.48\textwidth} 
	\centering
	\includegraphics[width=\textwidth]{KH_low_Wi_vary_Re} 
	\caption{}
	\label{fig:KH_reduce_Re} 
    \end{subfigure}

    \begin{subfigure}[b]{0.48\textwidth} 
	\centering
	\includegraphics[width=\textwidth]{KH_onset_beta_Wi} 
	\caption{}
	\label{fig:KH_elastic_onset} 
    \end{subfigure} ~
    \begin{subfigure}[b]{0.48\textwidth} 
	\centering
	\includegraphics[width=\textwidth]{fin_dispersions_Wi50} 
	\caption{}
	\label{fig:KH_finite_dispersions} 
    \end{subfigure} 
    \caption{ 
	a) The change in the height of the dispersion relation as $\Wi$ is
	increased at $\Rey = 0$ with $\Delta = 0.1$. The green and red lines gives
	the behaviour at $\beta=0.1$, $\beta=0.5$ respectively. b) The change in
	the height of the dispersion relation as the Reynolds number is reduced at
	$\Wi=5.0$. The colours give the values of $\beta$ as above, with blue being
	the behaviour for $\beta=0.9$. At low $\Rey$ the instability is clearly
	still present for large polymer concentrations, consistent with purely
	elastic turbulence with $\Delta = 0.1$.  c) The value of the Weissenberg
	number at which the velocity profile becomes unstable against $\beta$ at
	$\Delta = 0.1$.  The onset of the purely elastic instability moves to
	higher $\Wi$ as $\beta$ increases. d) Dispersion relations at Wi =50 for
	$\Delta =0.1$.  
    }
\end{figure}

\begin{figure} 
    \centering
    \includegraphics[width=0.7\textwidth]{growth_rate_sldim} 
    \caption{ 
	Phase diagram showing the growth rate for various values of the
	Reynold's and Weissenberg numbers at $\beta=0.1$. Grey lines represent
	lines of constant elasticity. Black squares are data points for which
	the flow is linearly stable.  
    } 
    \label{fig:vary_Re_delta_conv} 
\end{figure}

\section{Confirming the model}

@@

The finite extensibility version of the model gives good agreement with the
Oldroyd-B version. Shorter lengths bring about a larger instability but do not
delay it to higher Weissenberg number. Otherwise similar dispersion relations
are observed with a similar dependence on the distance to the walls (figure
\ref{fig:FENE_low_Re}).

\begin{figure} 
    \centering
    \includegraphics[width=0.7\textwidth]{FENE_purely_elastic} 
    \caption{ 
	The FENE-P model fluid at $\Rey = 0$  when $\Delta = 0.1$. Results are
	consistent with figure \ref{fig:KH_purely_elastic}.  
    }
	\label{fig:FENE_low_Re} \end{figure}

\subsection{Varying width of the instability}

\begin{figure} \centering
    \includegraphics[width=0.7\textwidth]{high_Re_vary_delta} 
    \caption{
	Dispersion relations for various values of $\Delta$ and $\Rey = 1000$,
	$\Wi = 0.01$. When results are rescaled for delta, The instability is
	found to be insensitive to the width of the instability relative to the
	wall at this combination of Reynold's number and Weissenberg number.  
    }
    \label{fig:delta_dispersion}
\end{figure}

\subsection{Drag reduction}

We see drag reduction using the Oldroyd-B model. It is not clear whether or not
the maximum drag reduction asymptote is present (figure
\ref{fig:KH_drag_reduction}).

\begin{figure}
%   \showthe\columnwidth %use this to determine size of figures.
    \centering \includegraphics[width=0.7\textwidth]{KH_high_Re_vary_Wi}
    \caption{ 
	Peak growth rate against Weissenberg number at $\Rey = 1000$,
	$\Delta = 0.1$ The height of the dispersion relation is reduced for the
	Kelvin-Helmholtz instability as the Weissenberg number is increased.
	The grey dashed line is the height of the dispersion relation for the
	Newtonian fluid. The decrease in $\lambda_{r}$ corresponds to increased
	stability of the base flow and so confirms the presence of drag
	reduction in this system.  
    } 
    \label{fig:KH_drag_reduction} 
\end{figure}

>>>>

%	paper.tex	Toby Searle
%	Last modified: Fri 12 Feb 11:52:33 2016
%	using jfm template

@@

\section{Problem formulation}\label{sec:KH_problem_formulation}

We propose that in fact, besides the shear banding instability and the
coextrusion instabilities, there is another mechanism by which a purely elastic
fluid may become unstable. Using a linear stability analysis we examine a new
Kelvin-Helmholtz like instability in both Oldroyd-B and FENE fluids. A purely
elastic fluid is found to be unstable at sufficiently high Weissenberg number.
The growth rate of the largest growing eigenmode of the instability increases
with increasing Weissenberg number at low Reynolds numbers and this behaviour
is consistent across both Oldroyd-B and FENE constituitive models.

The flow we consider is a hyperbolic tangent shaped laminar profile for the
streamwise velocity across a channel, where $y = \pm \Delta$ is the region of
shear. $y=0$ is the centreline of the channel, so that if $\Delta << 1$ the
flow can be said to be a free shear instability.  This gives a base flow
profile, 
\begin{align} 
    U(y) &= \tanh \left( y/\Delta
    \right) \coth \left( 1/\Delta \right) \nonumber\\ V &= 0 \nonumber \\
    T_{xx}(y) &= 2 Wi \left( \dy{U} \right)^{2} \nonumber \\ T_{xy}(y) &=
    \dy{U} \nonumber \\ T_{yy}(y) &= 0 \label{eq:KH_laminar_profile}
\end{align}
$U$ and $V$ are the base streamwise (x) and wall normal (y) velocities
respectively. $T$ is the base stress tensor. We use Gauss-Labatto points in the
wall-normal ($y$) direction for the base profile, and decomposed the
disturbances to this flow into Fourier modes.  
\begin{equation} 
    g(y) = \sum\limits_{n=-N}^{N} \widetilde{g}(y) e^{ikx + \lambda t} 
\end{equation}
for all disturbance variables $g = u, v, p, \tau_{i,j}$. Where $N$ is the
number of Fourier modes, $k$ is the streamwise wavenumber of the disturbance
and $\lambda$ is the growth rate of the mode. This program uses two domains of
pseudo-spectral points to give increased resolution in the centre of the
channel. The analysis was repeated using a code for which the system of points
was stretched using: 
\begin{align} 
    z_{u} &= \frac{y_{u}}{1-y_{u}} \\
    z_{b} &= \frac{y_{b}}{1+y_{b}} \\ U     &= \tanh{z/\Delta}
    \label{eq:KH_inf_profile} 
\end{align} 
This system ought to be completely insensitive to the boundary conditions at
the walls so we refer to it as 'free shear' throughout this manuscript.

The dimensionless quantities used throughout are non-dimensionalised relative
to the instability size, $\Delta$, rather than the half channel width. This is
because $\Delta$ is the length scale for the free shear instability.

We used an Oldroyd-B fluid with very low Reynolds number $\Rey \leq 1.0$ and a
small ratio between the solvent and total viscosities $\beta =
\frac{\mu_{s}}{\mu_{s}+\mu_{p}}$. This approximates a purely elastic fluid,
where the polymer contribution to the stress on the fluid is much larger  than
the solvent contribution. The Oldroyd-B Navier stokes and constitutive
equations are then: 
\begin{align} 
    Re \left[ \dt{\mathbf{v}} +
    \mathbf{v} \cdot \nabla  \mathbf{v} \right] &= - \nabla p + \beta
    \nabla^{2} \mathbf{v} + \frac{1-\beta}{Wi} \nabla \cdot \mathbf{\tau} \\
    \dot{\tau}/Wi + \overset{\nabla}\tau &= \left(\nabla \mathbf{v}\right)^{T}
    + \nabla{\mathbf{v}} 
\end{align} 
With $\mathbf{v}$ as the total (base flow and disturbance) velocity and $\tau$
as the total stress in the polymeric fluid. The FENE-P viscoelastic fluid has
the advantage of being similarly easy to analyse using our spectral method, but
also including a finite extensibility for the polymers. This leads to a stress
which depends on a conformation tensor ($\mathbf{C}$) for the polymer dumbbells
via a non-linear spring force:

\begin{equation} 
    \mathbf{\tau} = \frac{1-\frac{3}{L^{2}}}{1 +
	\frac{L^{2}}{tr(\mathbf{C^{2}})}} \label{eq:KH_FENE_stress}
\end {equation}

\begin{figure} 
    \centering 
    \includegraphics[width=0.3\textwidth]{{KH_diagram}}
    \caption{diagram of the system} 
    \label{fig:KH_diagram} 
\end{figure}

@@

\FloatBarrier

\section{Purely elastic linear stability analysis}\label{sec:KH_linear_stability_analysis}

At low Reynolds number, low $\beta$ and sufficiently large Weissenberg number
we observe a free shear instability across a range of streamwise disturbance
wavenumbers. This leads us to suppose that this instability might be a
plausible cause for a self-sustaining process in viscoelastic plane Couette
flow, similar to that observed by Waleffe for Newtonian flows.

We see an instability grow from around $k \sim 0.06$ and move to lower $k$ as
the Weissenberg number increases (figure \ref{fig:KH_inf_dispersions_vary_Wi}). The
height of the instability also increases with increasing Weissenberg number
(figure \ref{fig:KH_inf_disp_height_vary_Wi}).

\begin{figure} 
    \centering 
    \begin{subfigure}[b]{0.48\textwidth} 
	\centering
	\includegraphics[width=\textwidth]{{inf_purely_elastic}}
	\caption{}
	\label{fig:KH_inf_disp_height_vary_Wi} 
    \end{subfigure} ~
    \begin{subfigure}[b]{0.48\textwidth} 
	\centering
	\includegraphics[width=\textwidth]{{inf_dispersions_low_Re}} 
	\caption{}
	\label{fig:KH_inf_dispersions_vary_Wi} 
    \end{subfigure} 
    \caption{
	a) Free shear version of the instability. Plot of the maximum growth
	rate against Weissenberg number at $\Rey = 0.01$. b) Dispersion
	relations at various Weissenberg numbers to accompany the trend in
	figure a).
    } 
\end{figure}

@@

\begin{figure} 
    \centering 
    \begin{subfigure}[b]{0.48\textwidth} 
	\centering
	\includegraphics[width=\textwidth]{{inf_vary_Re}} 
	\caption{}
	\label{fig:KH_inf_disp_height_vary_Re} 
    \end{subfigure} ~
    \begin{subfigure}[b]{0.48\textwidth} 
	\centering
	\includegraphics[width=\textwidth]{{inf_dispersions_low_Wi}}
	\caption{}
	\label{fig:KH_dispersions_vary_Re} 
    \end{subfigure} 
    \caption{ 
	a) Free shear version of the instability. Plot of the maximum growth
	rate against Reynold's number with $\Wi=50$. b) Dispersion relations at
	various Reynold's numbers to accompany the trend in figure a).  
    }
\end{figure}

As the Reynold's number is reduced, new eigenvalues become dominant. Although
the dominant eigenvalue changes the flow is still unstable, even down to $\Rey
= 0.01$ (see figures \ref{fig:KH_inf_disp_height_vary_Re} and \ref{fig:KH_dispersions_vary_Re}).

\subsection{Shear instability with walls}

Now we use equations \ref{eq:KH_laminar_profile} and examine the unstretched
pseudospectral domain.  The instability remains present under variation of
$\Delta$ at low $\Delta$. At $\Delta =0.1$ the instability is still present for
$\Rey < 0.01$ far lower than the usual threshold of $\Rey \sim 1000$ for a
Newtonian Kelvin-Helmholtz instability (figure \ref{fig:KH_walls_vary_Re}).

At high Reynolds number the instability is insensitive to the distance to the
walls when $\Delta =0.1$ (figure \ref{fig:KH_high_Re_walls_dependence}). At low
Reynolds number, the width of the channel is more important but the instability
is still present for very low $\Delta$ (figure
\ref{fig:KH_low_Re_walls_dependence}).

\begin{figure} 
    \centering 
    \includegraphics[width=\textwidth]{{KH_vary_delta}}
    \caption{
	Dispersion relations for various values of $\Delta$ at $\Rey = 0.1$,
	$\Wi = 100$. The sensitivity to the walls seems only to increase the
	strength of the instability. Even when the system is insensitive to the
	walls, at $\Delta= 0.0125$, there is still an instability present.
    } 
    \label{fig:KH_low_Re_walls_dependence} 
\end{figure}

\begin{figure} \centering
    \includegraphics[width=0.7\textwidth]{{high_Re_vary_delta}}
    \caption{
	Dispersion relations for various values of $\Delta$ and $\Rey = 1000$,
	$\Wi = 0.01$. When results are rescaled, the instability is
	found to be insensitive for $\Delta =0.1$.
    }
    \label{fig:KH_high_Re_walls_dependence}
\end{figure}

If we examine the eigenvectors of the instability, we see that there are very
large polymer stresses in the $\pm \Delta$ region (figure
\ref{fig:KH_stress_low_delta}). This corresponds to the large shear rate
brought about as the two flows pass each other. Examining the flow field, we
see that there are large vortices arranged with opposite rotational directions
above and below the shear region which extend almost to the walls. This is a
very different situation from that observed for the Newtonian Kelvin-Helmholtz
instability, where there is an exponential decay in the velocity outside the
region of shear (figure \ref{fig:KH_Visco_Newt_evectors}). The larger
penetration depth out of the shear layer by the viscoelastic eigenvector is
likely linked to the stronger dependence on $\Delta$ relative to the Newtonian
instability.

\begin{figure}[h]
    \includegraphics[width=\textwidth]{{Visco_Newt_slice}.pdf}
    \caption{
	Streamfunction of the Newtonian Kelvin Helmholtz instability at $\Rey =
	1000$ compared with the purely elastic instability for $\beta = 0.1$,
	$\Rey = 0.0$, $\Wi = 5.0$, both at $\Delta =0.05$. The Newtonian Kelvin
	Helmholtz instability exponentially decays towards the channel walls
	whilst large vortices are present outside the walls in the purely
	elastic case.
    }
    \label{fig:KH_Visco_Newt_evectors}
\end{figure}

\begin{figure} \begin{subfigure}[b]{\textwidth} 
	\centering
	\includegraphics[width=\textwidth]{{psi_low_delta}}
	\caption{}
	\label{fig:KH_psi_low_delta}
    \end{subfigure} \vspace{1 mm}
    \begin{subfigure}[b]{\textwidth}
	\centering
	\includegraphics[width=\textwidth]{{txx_low_delta}} 
	\caption{}
	\label{fig:KH_stress_low_delta} 
    \end{subfigure} 
    \caption{
	a) Streamfunction of the largest eigenfunction of the instability when
	$\Rey = 0.1$, $\Wi =100$, $\Delta = 0.005$. Red is positive
	(streamlines of the flow point clockwise around the contours), Blue is
	negative (streamlines of the flow point anticlockwise around the
	contours) b) xx stress for the same instability.  
    }
\end{figure}

As $\Delta$ decreases for a particular purely elastic instability, the size of
the velocities expands slightly but in the limit of very small $\Delta$ the
eigenvector appears independent of the walls (figures
\ref{fig:KH_psi_low_delta} and \ref{fig:KH_psi_high_delta}). The large width
vortices in our purely elastic case, seem to correspond to the larger
elasticity ($G~\Wi/\Rey$) eigenvectors in \citet{Azaiez1994}. Their $G=5$ case
would only correspond to $\Wi=0.5$ for $\Re=0.1$ in our purely elastic
instability, so it is a completely different, inertial instability that they
observe (\citet{Azaiez1994} figure 8). Nonetheless at least one of their observations does apply. The fact
that the velocity disturbance is essentially zero in the center of the channel,
implies that the shear layer will be less likely to roll up. In the Newtonian
instability, net velocities within the shear layer will distort its shape,
however the purely elastic instability appears to have less of an effect on the
shear layer.

\begin{figure} 
    \centering 
    \includegraphics[width=\textwidth]{{psi_high_delta}}
    \caption{ 
	Streamfunction of the eigenfunction of the instability at $\Delta =
	0.1$, $\Wi = 100$, $\Rey=0.1$. The magnitude is scaled by the xx stress
	in the centre of the channel.  
    } 
    \label{fig:KH_psi_high_delta}
\end{figure}

@@

The analysis for the system in the channel has implications for the plane
Couette problem. The Kelvin-Helmholtz instability in the Newtonian problem
takes place on a length scale of about 10\% of the width of the channel, or
$\Delta = 0.1$. If this length scale is similar in the purely elastic case, we
can say that the viscoelastic Kelvin-Helmholtz instability is sensitive to the
walls at this $\Delta$ and a $\Rey \lesssim 1$ (see figure
\ref{fig:KH_disp_height_vary_Re_delta_conv}). This means that on the scale of
the channel, $\Rey \gtrsim 10$ for the walls not to affect the instability. So,
the important results for the purely elastic instability from the point of view
of the plane Couette problem are probably those for which the walls are
relevant.

\begin{figure} \centering
    \includegraphics[width=0.7\textwidth]{{vary_Re_delta_conv}}
    \caption{ The
	data in red corresponds to the free shear system and the green gives
	the $\Delta = 0.1$ data. By $\Rey = 1$ it is clear that the Reynold's
	number is sufficient such that the walled system behaves as though it
    were insensitive to the walls.  } \label{fig:KH_disp_height_vary_Re_delta_conv}
\end{figure}

\begin{figure} 
    \centering 
    \begin{subfigure}[b]{0.48\textwidth} 
	\centering
	\includegraphics[width=\textwidth]{{KH_low_Re_vary_Wi}}
	\caption{}
	\label{fig:KH_purely_elastic} 
    \end{subfigure} ~
    \begin{subfigure}[b]{0.48\textwidth} 
	\centering
	\includegraphics[width=\textwidth]{{KH_low_Wi_vary_Re}}
	\caption{}
	\label{fig:KH_walls_vary_Re} 
    \end{subfigure}

    \begin{subfigure}[b]{0.48\textwidth} 
	\centering
	\includegraphics[width=\textwidth]{{KH_onset_beta_Wi}}
	\caption{}
	\label{fig:KH_elastic_onset} 
    \end{subfigure} ~
    \begin{subfigure}[b]{0.48\textwidth} 
	\centering
	\includegraphics[width=\textwidth]{{fin_dispersions_Wi50}}
	\caption{}
	\label{fig:KH_finite_dispersions} 
    \end{subfigure} 
    \caption{ 
	a) The change in the height of the dispersion relation as $\Wi$ is
	increased at $\Rey = 0$ with $\Delta = 0.1$. The green and red lines gives
	the behaviour at $\beta=0.1$, $\beta=0.5$ respectively. b) The change in
	the height of the dispersion relation as the Reynolds number is reduced at
	$\Wi=5.0$. The colours give the values of $\beta$ as above, with blue being
	the behaviour for $\beta=0.9$. At low $\Rey$ the instability is clearly
	still present for large polymer concentrations, consistent with purely
	elastic turbulence with $\Delta = 0.1$.  c) The value of the Weissenberg
	number at which the velocity profile becomes unstable against $\beta$ at
	$\Delta = 0.1$.  The onset of the purely elastic instability moves to
	higher $\Wi$ as $\beta$ increases. d) Dispersion relations at Wi =50 for
	$\Delta =0.1$.  
    }
\end{figure}

\begin{figure} 
    \centering
    \includegraphics[width=0.7\textwidth]{{growth_rate_sldim}} 
    \caption{ 
	Phase diagram showing the growth rate for various values of the
	Reynold's and Weissenberg numbers at $\beta=0.1$. Grey lines represent
	lines of constant elasticity. Black squares are data points for which
	the flow is linearly stable.  
    } 
    \label{fig:KH_growth_rate_phase_diagram} 
\end{figure}

\FloatBarrier

@@

The finite extensibility version of the model gives good agreement with the
Oldroyd-B version. Shorter lengths bring about a stronger instability and do not
delay it to higher Weissenberg number. Otherwise similar dispersion relations
are observed with a similar dependence on the distance to the walls (figure
\ref{fig:KH_FENE_low_Re}).

\begin{figure} 
    \centering
    \includegraphics[width=0.7\textwidth]{{FENE_purely_elastic}} 
    \caption{ 
	The FENE-P model fluid at $\Rey = 0$  when $\Delta = 0.1$, ranging from
	$L=100$ (top curve), $L=500$ and the Oldroyd-B model in the bottom
	curve. Results are consistent with figure \ref{fig:KH_purely_elastic}.  
    }
	\label{fig:KH_FENE_low_Re} \end{figure}

We see the height of the instability decrease with increasing Weissenburg number, and this trend is stronger for smaller $\beta$ (figure \ref{fig:KH_drag_reduction}).

\begin{figure}
%   \showthe\columnwidth %use this to determine size of figures.
    \centering \includegraphics[width=0.7\textwidth]{{KH_high_Re_vary_Wi}}
    \caption{ 
	Peak growth rate against Weissenberg number at $\Rey = 1000$,
	$\Delta = 0.1$ The height of the dispersion relation is reduced for the
	Kelvin-Helmholtz instability as the Weissenberg number is increased.
	The grey dashed line is the height of the dispersion relation for the
	Newtonian fluid. The decrease in $\lambda_{r}$ corresponds to increased
	stability of the base flow, this matches the observations made in \cite{Azaiez1994}} 
    \label{fig:KH_drag_reduction} 
\end{figure}

\FloatBarrier
